paper

### 2024-09-25 inst/extdata/paperdata/paper.qmd
.

## Columbia Case Study

@@

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
load("D:\\MJFF\\MJFF V2 10.30.2023\\proteogenomic study\\soma.rda")
print(soma)

@@

# Set metadata and formula for LimROTS analysis
meta.info <- c("group_comp" , "gender" , "AGE") 
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 10  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

saveRDS(limrots.result, "inst/extdata/paperdata/soma.LimROTS.rds")
```

@@

```{r}
plot(limrots.result$q_values)
hist(limrots.result$q_values)
hist(limrots.result$q_values$qvalues)

@@

@@

```{r}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("Columbia.RealCase")
data <- assay(Columbia.RealCase)
formula.str <- "~ 0 + groups + Age + gender + LRRK2.status + GBA.status"
meta.info <- data.frame(colData(Columbia.RealCase), check.names = FALSE, row.names = row.names(colData(Columbia.RealCase)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("groups1-groups2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="groups1-groups2" , number = "Inf")

@@

@@

rots <- ROTS(data, groups = as.numeric(meta.info$groups), B = 1000, progress = TRUE,
             K = 600, a1= 5, a2 = 1)
```

>>>>

## Proteogenomic PD Case Study

@@

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("proteogenomicPD")
print(soma)

@@

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

soma@colData@listData[["CNO"]] <- paste0("CNO" , soma@colData@listData[["CNO"]])

soma@colData@listData[["CNO"]] <- as.factor(soma@colData@listData[["CNO"]])

@@

# saveRDS(limrots.result, "inst/extdata/paperdata/proteogenomicPD.LimROTS.rds")
```

@@

```{r}
plot(limrots.result$q_values)
hist(limrots.result$q_values)
hist(limrots.result$q_values$qvalues)
hist(limrots.result$FDR)

@@

```{r}
limrots.result.df <- data.frame(proteins = row.names(limrots.result$data),
                                LimROTS.FC = limrots.result$corrected.logfc,
                                q = limrots.result$q_values$qvalues)
limrots.result.df <- limrots.result.df[limrots.result.df$q < 0.05,]
```

@@

```{r}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("soma")
data <- assay(soma)
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"
meta.info <- data.frame(colData(soma), check.names = FALSE, row.names = row.names(colData(soma)))
meta.info$sample.id <- NULL
meta.info$CNO <- as.factor(meta.info$CNO)
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("group_comp1-group_comp2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="group_comp1-group_comp2" , number = "Inf")

@@

length(which(limma.result$adj.P.Val < 0.05))

@@

rots <- ROTS(data, groups = as.numeric(meta.info$group_comp), B = 1000, progress = TRUE,
             K = 600, a1= 5, a2 = 1)
```
